\documentclass[11pt,a4paper]{article}

% 包导入
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{changepage}
\usepackage{graphicx}

% 页面设置
\geometry{margin=1in}

% 超链接设置
\hypersetup{    
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

% 标题格式设置
\titleformat{\section}{\Large\bfseries}{}{0em}{}
\titleformat{\subsection}{\large\bfseries}{}{0em}{}

% 文档信息
\title{\textbf{CS Group 8 TinyBridge Process Update \#4}}
\author{}
\date{December 2, 2025}

\begin{document}

\maketitle

\begin{center}
\textbf{TinyBridge} - A Lightweight URL Shortening Service designed for Efficiency and Branding.
\end{center}

\vspace{1em}

\section{Summary of Work Done to Date}

\begin{adjustwidth}{1.5em}{}
Since Update \#3, the team has successfully completed all planned features and achieved key milestones:

\subsection{1. QR Code Generation ---- Completed}

Implemented dynamic QR code generation for short links with customization styling options. Users can now generate QR codes directly from the dashboard with support for multiple formats (PNG, SVG) and size configurations.

\subsection{2. Click Analytics Dashboard ---- Completed}

Developed comprehensive analytics dashboard featuring real-time click tracking, geographic distribution visualization, device/browser statistics, and time-series charts. The dashboard provides actionable insights through intuitive data visualization components.

\subsection{3. Batch Operations API ---- Completed}

Finalized RESTful batch API endpoints supporting bulk link creation, modification and deletion. Implemented rate limiting and pagination for large-scale operations, with comprehensive API documentation for developer integration.

\subsection{4. System Testing \& Performance Optimization ---- Completed}

Conducted extensive load testing achieving \textbf{5,000+ requests/second} throughput. Stress testing validated system stability under peak loads. Identified and resolved performance bottlenecks through profiling, resulting in:

\begin{itemize}[leftmargin=*]
    \item Average response time: < 50ms
    \item Cache hit rate: 90\%+
    \item System up-time: 99.9\%
\end{itemize}

\subsection{5. Technical Report ---- Completed}

Finalized comprehensive technical report documenting system architecture, implementation decisions, algorithm designs, and testing methodologies. The report provides detailed analysis of technology choices and serves as reference documentation for the project.

\end{adjustwidth}

\section{Challenges Faced and Solutions}

\begin{adjustwidth}{1.5em}{}
\subsection{Challenge 1: Documentation Completeness Under Time Pressure}

With the final presentation approaching, ensuring comprehensive technical documentation while maintaining development momentum proved challenging. Balancing detail with clarity required careful prioritization.

\vspace{0.5em}
\noindent\textbf{Solution}: Adopted a modular documentation approach, leveraging existing white paper content as foundation. Assigned dedicated team members for documentation tasks with clear templates and style guides. Used automated tools to generate API documentation from code annotations.

\subsection{Challenge 2: Demo Scenario Preparation}

Creating compelling demo scenarios that effectively showcase TinyBridge's full capabilities within limited presentation time required strategic planning.

\vspace{0.5em}
\noindent\textbf{Solution}: Identified key user journeys (link creation, analytics review, team collaboration) and prepared scripted demonstrations. Created backup demo environments to mitigate live demo risks. Rehearsed presentations to optimize timing and flow.
\end{adjustwidth}

\section{Next Steps}

\begin{adjustwidth}{1.5em}{}
\begin{enumerate}[leftmargin=*]
    \item \textbf{Final Presentation Preparation}: Complete presentation slides, rehearse demo scenarios and prepare for Q\&A session. Ensure all team members are familiar with system architecture and implementation details.

    \item \textbf{Project Deliverables Finalization}: Package all documentation (white paper, technical report, API docs) for final submission. Prepare deployment guide and user manual for potential future maintainers.

    \item \textbf{Post-Project Review}: Conduct team retrospective to document lessons learned, evaluate what worked well and identify areas for improvement in future projects.
\end{enumerate}
\end{adjustwidth}

\vspace{1em}

\begin{flushright}
\textbf{Date}: December 2, 2025 \\
\textbf{Team}: CS Group 8
\end{flushright}

\end{document}
